Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/type-theory.tex
[ paper ] more corrections.
[ paper ] added strip reference to the appendix.

Type theory is a formalism [TODO]

Even though we choose a proof-assistant for type theory
where proof verification becomes a type-checking task of the proof-term following the Curry-Howard isomorphism.

Therefore the proof-reconstruction tool generates proof-terms by reconstructing the proof using the formalization
the prover in type theory. However, this approach suffers from some limitations of type theory as we describe in Section~\ref{sec:type-theory}.

@@

\begin{equation}
\label{eq:uh-definition}
\begin{aligned}
&\hspace{.495mm}\fuh_{0} : \Prop → \Prop\\
&\begin{array}{lll}
  \fuh_{0} &(φ₁ ⇒ (φ₂ ⇒ φ₃)) &= \fuh_{0}~((φ₁ ∧ φ₂) ⇒ φ₃)\\
  \fuh_{0} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &= \fuh_{0}~(φ₁ ⇒ φ₂) ∧ \fuh_{0}~(φ₁ ⇒ φ₃)\\
  \fuh_{0} &φ                &= φ
\end{array}
\end{aligned}
\end{equation}

@@

\begin{equation}
\label{eq:uh-structured}
\begin{aligned}
&\hspace{.495mm} \fuh_{1} : \Prop → \Nat \to \Prop\\
&\begin{array}{llll}
\fuh_{1} &(φ₁ ⇒ (φ₂ ⇒ φ₃)) &(\suc~n) &= \fuh_{1}~((φ₁ ∧ φ₂) ⇒ φ₃)~n\\
\fuh_{1} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &(\suc~n) &= \fuh_{1}~(φ₁ ⇒ φ₂)~n ∧ \fuh_{1}~(φ₁ ⇒ φ₃)~n\\
\fuh_{1} &φ &n &= φ
\end{array}
\end{aligned}
\end{equation}

@@

\begin{equation}
% \label{eq:rank-definition}
\begin{aligned}
&\hspace{.495mm}\frank : \Prop → \Nat\\
&\begin{array}{llll}
\frank~(¬~φ)           &= \frank~φ₁~+~c_{¬}\\
\frank~(φ₁~\square~φ₂) &= \fmax~(\frank~φ₁)~(\frank~φ₂) + c_{\square}\\
\frank~φ               &= 0
\end{array}
\end{aligned}
\end{equation}

@@

\begin{equation}
  \label{eq:uh-complexity}
  \begin{aligned}
    &\hspace{.495mm}\fuh_{cm} : \Prop → \Nat\\
    &\begin{array}{llll}
    \fuh_{cm}~(φ₁ ⇒ (φ₂ ⇒ φ₃)) &= \fuh_{cm}~φ₃ + 2\\
    \fuh_{cm}~(φ₁ ⇒ (φ₂ ∧ φ₃)) &= \fmax~(\fuh_{cm}~φ₂)~(\fuh_{cm}~φ₃) + 1\\
    \fuh_{cm}~φ                &= 0
    \end{array}
  \end{aligned}
\end{equation}

@@

\subsection{Intuitionistic logic (ESCRIBIENDO)}
\label{ssec:intuitionistic-logic}

>>>>

% Type theory is a formalism [TODO]

% Even though we choose a proof-assistant for type theory
% where proof verification becomes a type-checking task of the proof-term following the Curry-Howard isomorphism.

% Therefore the proof-reconstruction tool generates proof-terms by reconstructing the proof using the formalization
% the prover in type theory. However, this approach suffers from some limitations of type theory as we describe in Section~\ref{sec:type-theory}.

@@

\begin{equation}
\label{eq:uh-definition}
\begin{aligned}
&\hspace{.495mm}\fuh_{0} : \Prop → \Prop\\
&\begin{array}{lll}
  \fuh_{0} &(φ₁ ⇒ (φ₂ ⇒ φ₃)) &= \fuh_{0}~((φ₁ ∧ φ₂) ⇒ φ₃)\\
  \fuh_{0} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &= \fuh_{0}~(φ₁ ⇒ φ₂) ∧ \fuh_{0}~(φ₁ ⇒ φ₃)\\
  \fuh_{0} &φ                &= φ.
\end{array}
\end{aligned}
\end{equation}

@@

\begin{equation}
\label{eq:uh-structured}
\begin{aligned}
&\hspace{.495mm} \fuh_{1} : \Prop → \Nat \to \Prop\\
&\begin{array}{llll}
\fuh_{1} &(φ₁ ⇒ (φ₂ ⇒ φ₃)) &(\suc~n) &= \fuh_{1}~((φ₁ ∧ φ₂) ⇒ φ₃)~n\\
\fuh_{1} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &(\suc~n) &= \fuh_{1}~(φ₁ ⇒ φ₂)~n ∧ \fuh_{1}~(φ₁ ⇒ φ₃)~n\\
\fuh_{1} &φ &n &= φ.
\end{array}
\end{aligned}
\end{equation}

@@

\begin{equation}
% \label{eq:rank-definition}
\begin{aligned}
&\hspace{.495mm}\frank : \Prop → \Nat\\
&\begin{array}{llll}
\frank~(¬~φ)           &= \frank~φ₁~+~c_{¬}\\
\frank~(φ₁~\square~φ₂) &= \fmax~(\frank~φ₁)~(\frank~φ₂) + c_{\square}\\
\frank~φ               &= 0.
\end{array}
\end{aligned}
\end{equation}

@@

\begin{equation}
  \label{eq:uh-complexity}
  \begin{aligned}
    &\hspace{.495mm}\fuh_{cm} : \Prop → \Nat\\
    &\begin{array}{llll}
    \fuh_{cm}~(φ₁ ⇒ (φ₂ ⇒ φ₃)) &= \fuh_{cm}~φ₃ + 2\\
    \fuh_{cm}~(φ₁ ⇒ (φ₂ ∧ φ₃)) &= \fmax~(\fuh_{cm}~φ₂)~(\fuh_{cm}~φ₃) + 1\\
    \fuh_{cm}~φ                &= 0.
    \end{array}
  \end{aligned}
\end{equation}

@@

\subsection{Intuitionistic logic}
\label{ssec:intuitionistic-logic}
